---
title: "Orientation to `{devoirs}`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Orientation to `{devoirs}`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(devoirs)
```

The `{devoirs}` package for R provides a full suite of utilities for writing course assignment documents, collecting student answers, and viewing and scoring those answers by instructors. Work with `{devoirs}` is structured into three largely independent phases to support collaboration among authors and instructors.

Since different people may be involved in the different phases, documentation for each phase is provided in its own vignette. Short descriptions are given in the following. 

If you are reading this document, you may already have installed R, RStudio, and the `{devoirs}` package. If not ... Instructions for installing R and RStudio are widely available on the internet. To install or update the `{devoirs}` package, use this command:

```r
# install.packages("remotes") # if you don't have `{remotes}`
remotes::install_github("dtkaplan/devoirs", build_vignettes = TRUE)
```

## Phase 1: Writing assignment documents

Student work for a course is made available via one or more **assignment documents**. 

Assignment documents are written in Quarto and compiled to HTML.

Deploying the HTML documents can be done using any web-server or a "course support" system such as Moodle or Canvas. The system is decentralized and allows, for instance, assignment documents provided by a textbook as well as assignment documents provided by instructors to be intermixed at will.

## Phase 2: Collecting student answers

The assignment documents written in Phase 1 contain editor widgets where students can compose their answers to individual prompts in the assignment. There are also radio-button widgets for multiple-choice questions.

Each assignment document contains a widget that students can use to collect *all* the answers in a document, formatting these in a string that is copied to the student's clipboard.

The instructor (not the author) sets up a **collection facility** such as a Google Form into which the student can paste the answer string from the clipboard. This collection facility, not `{devoirs}`, will handle all student authentication.

## Phase 3: Viewing & scoring student answers

For each course (or whatever granularity the instructor chooses), there is a **grading directory** on the instructor's computer. This will typically be set up at the start of a semester, although it is perfectly possible to use a *grading directory* across multiple semesters. With multiple instructors, it may be desirable to set up a single grading directory in a shared disk space.

At the instructor's request, student answers are downloaded from the *collection facility*. This is done incrementally, updating storage files in the *grading directory*.

Two shiny apps are provided. `ScoreEssays()` allows essay answers to be given a score, `ViewDocument()` consolidates all student submissions for one assignment document at a time.




