---
title: "Writing and collecting homework with the `{devoirs}` package "
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Writing and collecting homework with the `{devoirs}` package }
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r include=FALSE}
library(devoirs)
```

Instructors routinely write homework assignments and collect student answers. For those instructors distributing assignments as HTML files using the Quarto system to produce them, the lightweight `{devoirs}` package^[*devoirs* is French for "homework."] lets you instrument the HTML file so that student answers can easily be submitted and provides a responsive "multiple-choice" format.

Unfortunately, R vignettes do not yet support Quarto, so the vignette contents are contained in this [blog post].

The overall structure of a Quarto `.qmd` file that uses `{devoirs}` has three elements:

1. A chunk near the start of the document to load the `{devoirs}` library:

```{r}
#| echo: fenced
library(devoirs)
```

2. A chunk (typically at near the start of the document) that provides the facility to collect the student answers in a format that can be pasted into whatever web-based collection facility you use, for example, Google Forms. The render output from `devoirs_start()` the 
     
```{r eval=FALSE}
#| echo: fenced
devoirs_start(documentID = "June 3 blog post", 
              collectURL = "<an actual URL>") 
```
     
```{r echo=FALSE, results="asis"}
devoirs_start(documentID = "June 3 blog post", 
              collectURL =
"https://docs.google.com/forms/d/e/1FAIpQLSevJgyHTRHm6_HVQqrYMd8wjMYifPknPLXtpVTunlWlO7RbMw/viewform?usp=pp_url")
```
     
In action, this specific vignette file links to a Google Form, but the instructor needs to
provide her own such facility via the `collectURL` argument.



3. At the end of the document (after any `{devoirs}` questions) a closing statement that provides the necessary javascript functionality to power the answer collection:

```r devoirs_end()```

Between the `devoirs_start()` and `devoirs_end()` markers, you can add as many questions as you want. Each question must be given a unique ID.

## Multiple-choice question: Example

What color is the blue moon? 

     ``{mcq}
     #| label: blue-moon
     #| inline: true
     #| show_hints: true
     1. blue [hint: It's not blue!]
     2. red $\sqrt{3}$
     3. moon colored [correct]
     ```

The individual items are numbered (or provided with any other kind of label ending with a period). This label will not be printed out.

Options are set using the inline-yaml style.

To turn on showing hints globally, as when producing an answer key, create a 
global variable `devoirs_show_hints` and set to `TRUE`.

## Essay question: Example

Write something of interest!

     `` r devoirs_text("of-interest")``


## 



`r devoirs_end()`


